\section{Conclusion}
\label{sec:conclusion}

\textit{[Synthesizes the paper's six contributions and their deployment implications.
Paragraph 1: VP proximity is the binding constraint at global scale; the operator's first lever is
deploying VPs co-located with target ASN infrastructure. The proximity-sufficient regime is where
CBG variants diverge, and where the bounded answer space does the most work (53--68\% tolerance
dividend in the US matched-regional setup).
Paragraph 2: The failure taxonomy (EMPTY/EXCLUSIVE/INCLUSIVE) and the three-lever feature model
(proximity, answer-space isolation, angular surround) give operators a diagnostic interface for any
CBG variant. At $R = 50$\,km, EXCLUSIVE is large for annulus variants (Octant $\approx$50\%,
Spotter $\approx$89--99\%) but classification accuracy survives via EXCLUSIVE-but-correct centroid
snapping; this is the core mechanism behind the tolerance dividend. For disk variants (Vanilla,
Million-scale), INCLUSIVE misclassification is the dominant failure, making centroid resolution
the remaining bottleneck.
Paragraph 3: Geometric centroid is the production-ready default — 20$\times$ throughput over Monte
Carlo with equal or better accuracy. Per-ASN calibration is mandatory; pooled training corrupts the
LTD model. The composable open-source framework lets future CBG accuracy claims be pinned to a
specific (P1, P2, P3) triple.]}

% PAPER-FLOW (implied)
% Summary: VP proximity dominates at global scale; operators should deploy VPs co-located with
% target ASN infrastructure (proximity-sufficient regime) where CBG classification accuracy
% reaches 40–51% over a bounded-candidate answer space.
%
% Key takeaways:
%   1. Proximity is the binding constraint. When the nearest VP is >1,000 km from the truth
%      centroid, no CBG variant outperforms a random baseline meaningfully.
%   2. At operator scale (VP fleet co-located with target ASN), the bounded answer space does
%      substantial work: 53–68% of all correct answers are wins from answer-space tolerance
%      alone (tolerance dividend), invisible to coordinate-error metrics.
%   3. Failure mode at operator scale depends on variant: annulus variants (Octant ~50%,
%      Spotter ~89-99% EXCLUSIVE); disk variants (Vanilla, MS: INCLUSIVE-dominant). EXCLUSIVE
%      predictions can still snap to the right cell (EXCLUSIVE-but-correct = tolerance mechanism).
%   4. Geometric centroid at ~0.25 ms vs. Monte Carlo at 190–390 ms: 20× throughput,
%      equal or better accuracy. Deploy geometric centroid at production scale.
%   5. Per-ASN calibration is mandatory; pooled-ASN training degrades accuracy by corrupting
%      the LTD model with mixed propagation topologies.
%
% Future work: extend to IPv6 targets, evaluate on additional operator fleets, characterize
% the physics-validation primitive's intersection-cardinality distribution in production.
%
% [TODO: write 2–3 paragraphs synthesizing findings and implications]
