\section{Improved CBG Variants}
\label{sec:improved}

% PAPER-FLOW §7
% Given §6's failure taxonomy, we ask: do targeted repairs to each variant's failure mode
% produce a better variant? Evaluation: classification accuracy across all setups.
% No new metrics introduced. Closes with head-to-head of best new combo vs. original four.
%
% §7.1 Weighted vs. unweighted intersection:
%   vanilla_cbg → vanilla_cbg_geo (planar_annulus_weighted + geometric_centroid)
%   million_scale_cbg → million_scale_cbg_geo (same)
%   octant_cbg → octant_cbg_top (highest_weight_only)
%   spotter_cbg → spotter_cbg_top (same)
%   Question: does weighting repair EXCLUSIVE and INCLUSIVE misclassification, and for which
%   variants / regimes?
%
% §7.2 Geometric vs. Monte Carlo centroid:
%   octant_cbg → octant_cbg_top_geo (Monte Carlo → geometric)
%   spotter_cbg → spotter_cbg_top_geo
%   Directly targets INCLUSIVE resolution failures (Phase 3). Production cost payoff: §6.5.
%
% §7.3 Tight vs. loose constraint (Octant hull variants):
%   octant_cbg_geo (tight, standard) vs. octant_cbg_hull_geo (hull-relaxed, loose)
%   Loosening reduces EMPTY and EXCLUSIVE at cost of resolution coarseness.
%   Question: does loosening recover EMPTY failures without introducing new INCLUSIVE errors?
%
% §7.4 Head-to-head:
%   Best new combo across all setups vs. the four textbook baselines.
%   [Results TBD — data exists in outputs/global_as16509_final + final country runs.]

\subsection{Weighted Intersection}
\label{sec:improved-weighted}
% TODO
\textit{[Compare: vanilla\_cbg → vanilla\_cbg\_weighted (annulus-weighted);
million\_scale\_cbg → million\_scale\_cbg\_weighted; octant\_cbg → octant\_top (top constraint);
spotter\_cbg → spotter\_top (top constraint).
Question: does weighting repair INCLUSIVE misclassification and EXCLUSIVE, and for which variants?
Data lives in \texttt{outputs/} for all improved combos.]}

\subsection{Geometric vs. Monte Carlo Centroid}
\label{sec:improved-centroid}
% TODO
\textit{[Holding MTL fixed, swap centroid rule: octant\_cbg $\to$ octant\_cbg\_geo;
spotter\_cbg $\to$ spotter\_cbg\_geo. Directly targets Phase 3 INCLUSIVE resolution failures.
Production-cost payoff already shown in §\ref{sec:results-cost} ($20\times$ throughput);
here we quantify the accuracy trade-off.]}

\subsection{Tight vs. Loose Constraint}
\label{sec:improved-constraint}
% TODO
\textit{[Holding centroid = geometric, compare Octant constraint tightness:
octant\_cbg\_geo (standard, tight) vs.\ octant\_hull\_geo (hull-relaxed, loose).
Loosening reduces EMPTY\_REGION and EXCLUSIVE at cost of resolution coarseness.
Does loosening recover EMPTY failures without introducing new INCLUSIVE misclassifications?
Front-runner result: octant\_hull\_geo 30.0\% / 65 targets/s beats octant\_cbg 25.2\% / 3.2 targets/s.]}

\subsection{Head-to-Head Comparison}
\label{sec:improved-head2head}
% TODO
\textit{[Best new combo across all setups vs.\ the four textbook baselines.
Current front-runner: \texttt{octant\_hull\_geo} (geometric centroid + hull-relaxed annulus) —
30.0\% at 65 targets/s globally, beating default Octant at 25.2\% / 3.2 targets/s.
Table: all setups × all variants (textbook + improved), classification accuracy.
TO BE FINALIZED after §7.1--§7.3 are computed.]}
