\section{Dataset and Experimental Setup}
\label{sec:setup}

% PAPER-FLOW §5
% Covers: (a) two datasets with different roles; (b) the bounded-answer-space task construction;
% (c) the physics-validation primitive (SoI intersection); (d) evaluation metrics.
%
% §5.1 Dataset characteristics:
%   - Public RIPE-based dataset: 713 anchors, three ASN fleets (AS16509/30 global VPs,
%     AS7018/125 US VPs, AS3209/164 EU VPs), 5-fold cross-validation.
%     Limitation: sparse per-ASN anchor counts (no single target ASN > 7 anchors in US).
%   - Proprietary operator dataset: user-plane/mobile-core RTTs, one target ASN,
%     200+ IPs across 20+ US clusters, VP topology matched to public dataset.
%
% §5.2 Data processing and setup construction:
%   - Target clustering: complete-linkage agglomerative, R=50 km, 257 global / 32 US / 21 DE cells.
%   - VP grouping by ASN + geographic scope.
%   - Geometry maps per setup (VP locations, centroid cells, fleet geometry diagnostics).
%   - K-fold: (K-1)/K anchor folds → LTD calibration; held-out fold → eval targets.
%
% §5.3 Validation primitive — Speed-of-internet intersection (calibration-free):
%   SoI circle: C_v = { x : dist(v,x) ≤ (2/3)c · RTT/2 }.
%   Physics-consistent iff claim ∈ ⋂_v C_v (unanimous; relax to majority for congested VPs).
%   Tradeoff: SoI-consistent ≠ uniquely identified (multiple candidate sites may be inside).
%   Bootstraps Anchored-track training from Geofeed/rDNS records.
%
% §5.4 Metrics:
%   - Classification accuracy (same-centroid, primary)
%   - within-R rate (coordinate proxy)
%   - Tolerance dividend = same_centroid_acc − within_r
%   - fleet_abs_km = d(V*, C): closest VP to truth centroid
%   - target_distinguishable_vp_margin = d(C,N)/2 − fleet_abs_km (triangle-inequality threshold)
%   - Shortest-ping baseline (RTT-based VP-location snap)
%   - Practicality: runtime and memory by phase

\subsection{Datasets}
\label{sec:setup-datasets}
% TODO
\textit{[Two datasets with complementary roles.
Public RIPE: 713 anchors, RTTs from three ASN fleets (AS16509 / 30 global VPs, AS7018 / 125 US VPs,
AS3209 / 164 EU VPs); reproducible and public but noisy for the operator question (sparse per-ASN
anchor counts — no single target ASN contributes $>7$ anchors in the US).
Proprietary: user-plane/mobile-core RTTs from one operator toward a single target ASN,
200+ IPs across 20+ US clusters; cleanest operator regime (one operator ASN to one target ASN).
VP topology between datasets matched on VP count, geographic spread, and pairwise distance distribution.]}

\subsection{Setup Construction and Answer Space}
\label{sec:setup-construction}
% TODO
\textit{[Bounded-answer-space construction: ground-truth coordinates clustered via complete-linkage
agglomerative clustering at $R = 50$\,km. Yields 257 global / 32 US / 21 DE answer cells.
Each cell has a centroid; a prediction is correct iff it snaps to the truth's centroid.
Five VP-target setups: global-global (AS16509), US-global (AS7018→713), EU-global (AS3209→713),
US-home (AS7018→96 US targets), DE-home (AS3209→96 DE targets).
5-fold cross-validation: $(K-1)/K$ folds calibrate LTD; held-out fold evaluates targets.]}

\subsection{Physics-Validation Primitive}
\label{sec:setup-soi}
% TODO
\textit{[Speed-of-Internet (SoI) circle per VP: $C_v = \{x : d(v,x) \leq \tfrac{2}{3}c \cdot \text{RTT}(v,T)/2\}$.
A claimed target location is \emph{physics-consistent} iff it lies inside at least $k$ of $N$ VP circles
(default $k = N$; relax to majority for congested VPs).
Calibration-free: runs on operator-owned VP locations without labeled training data.
Bootstraps Anchored-track training: Geofeed/rDNS records validated by SoI become labeled RTT-distance pairs.
Trade-off: SoI-consistent $\neq$ uniquely identified; multiple candidate sites may fall inside $\bigcap_v C_v$.]}

\subsection{Evaluation Metrics}
\label{sec:setup-metrics}
% TODO
\textit{[Primary: classification accuracy (same-centroid) and shortest-ping VP baseline.
Continuous proxy: within-$R$ rate (predicted point within 50 km of truth centroid).
Gap metric: \emph{tolerance dividend} = same\_centroid\_acc $-$ within\_$R$; measures answer-space tolerance wins.
Fleet geometry: \texttt{fleet\_abs\_km} = $d(V^*, C)$; \texttt{target\_distinguishable\_vp\_margin} = $d(C,N)/2 - d(V^*,C)$.
Inference-time confidence: L1 (MTL region overlaps exactly one answer cell) achieves precision 0.66--0.91.
Practicality: per-phase runtime (p50 ms/target) and throughput (targets/s).
All metrics reported per variant × setup; key contrast is classification accuracy vs. within-$R$..]}
